The paper on blockchain front-running

### 2018-09-25 frontrunning/Latex/sections/paper.tex
[frontrunning] full round edit

An early use of commit/reveal is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}. A user sends a commit transaction, which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.

In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal. This mitigation seems to require further research. One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal. Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early. One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{mccorry2017smart}). Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}. Using sealed votes, voters can make sure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.

Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, It will be obvious that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter. Also, this scheme means two transactions are required for a functionality which makes it more expensive.

@@

\paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} extend basic commit/reveal functionality with additional properties. In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized. With submarine send, it is possible to hide sender, receiver, value, and data, the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants. The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase. By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}. See Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.

@@

\item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run. To the same end, Malinova~\cite{malinova2017market} propose a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.

>>>>

An early use of commit/reveal is Namecoin, a Bitcoin-forked blockchain for name services~\cite{kalodner2015empirical}. In Namecoin, a user sends a commit transaction which commits to the name hash, similar to a sealed bid. Once the transaction is confirmed and the grace period is over, the user sends a reveal transaction revealing the bid and also the details of the requested domain~\cite{kalodner2015empirical}. Using this scheme, one is able to hide information from the adversarial parties in the system and prevent them from front-running.

In the case of decentralized exchanges, users can use commit/reveal for bids, where commitments are placed in an ordered queue and executed in a later round after a reveal. This mitigation seems to require further research. One trader strategy is to flood orders at the commitment stage, but then only selectively and adaptively choose which to reveal. Collateralization is another challenge, where revealed bids may simply be intentions to execute but additional transactions are required to move the money or tokens; a transaction that can also be aborted early. One mitigation to early aborts is having users post a fidelity bond that can be automatically dispensed if they fail to fully execute committed transactions (as used in~\cite{mccorry2017smart}). Commit/reveal is also seen in on-chain voting~\cite{adChainPLCRVoting}. Using sealed votes, voters can assure their votes are hidden until a later date, however, their participation and weight of the vote are publicly known.

Other than the collateralization issue for the commit and reveal scheme, another obvious issue is the participatory factor. For anyone watching the DApp address, there will be a direct transaction from the user to the DApp address, revealing the fact that a specific address has participated in the auction or the DApp using a commit and reveal scheme, but the details are hidden through the scheme. Both these issues, albeit hiding the details of the order and preventing direct front-running, leak information to other participants which could lead to more sophisticated front-running attacks depending on the application design. On the other note, these method has some drawbacks, the user experience is not smooth and one might forget to reveal the committed transaction. In the ENS commit-reveal process, if one forgets to reveal in the reveal phase, the committed funds are burnt and inaccessible thereafter. Also, this scheme means two transactions are required for a functionality which makes it more expensive.

@@

\paragraph{Design Decision \#2: Submarine Commitments.}\label{submarineCommits}
Submarine Commitments~\cite{breidenbach2018enter, submarinesendHD} extend basic commit/reveal functionality with additional properties. In particular, they hide the DApp being invoked during the commit phase and also ensure that revealed transactions that send funds are fully collateralized. With submarine send, it is possible to hide sender, receiver, value, and data, so the commitment transaction is identical to a transaction to a newly generated address. Submarine sends could be a solution for sealed-bid auctions on the blockchain to hide the existence of the bids for other participants. The details of how Submarine commitments work could fill an entire paper, however in short, using the way Ethereum transactions are constructed and ECDSA ECRecover functionality, it is possible to generate one outgoing transaction from an address of which no private key exists. By constructing a transaction from that address to the DApp and funding that address we fulfill the commitment phase. By revealing the details and broadcasting the constructed transaction we reveal the commitment~\cite{libsubmarine}. See Figure~\ref{fig:LibSubmarine}. However, this could be designed in other ways to suit the need of the DApp. Drawbacks of this scheme are similar to commit/reveal, with the addition of two more transactions to finalize a transaction, which adds cost and complexity to the user experience.

@@

\item \emph{Disincentivizing Front-running Actors:} The call market solution also pivots profitable gains that front-running miners stand to gain into fees that they collect~\cite{clark2014decentralizing}, removing the financial incentive to front-run. To the same end, Malinova~\cite{malinova2017market} proposes a design for a decentralized exchange which uses economic models in their trading market design to make front-running expensive and more costly than profitable. They split big investments into smaller ones using intermediaries --liquidity demander-- and liquidity providers to achieve this.
